Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-06-29 main.tex
Updates from Overleaf

\documentclass[twocolumn,astrosymb]{aastex631}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

@@

\author{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

\section{Methodology}
\subsection{Source Detection}\label{subsec:detection}
\citetalias{Greco2018} performed a search for extended LSBGs in the first $\sim 200$ deg$^2$ of HSC survey. We continued the work in \citetalias{Greco2018} and extended the search to HSC \code{S18A} data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to \code{S16A}. We follow the same philosophy of source detection as in \citetalias{Greco2018}, but make several updates to accommodate \code{S18A} data. Below we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer interested readers to \citetalias{Greco2018} for more details. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} is also publically available.

@@

    %Unlike in \citetalias{Greco2018}, we do not smooth the image prior to thresholding. 
    After this step, there are still a number of small low surface brightness objects, which are typically marginally resolved galaxies or just pixels with high noise fluctuations. We detect and remove them since our main goal is to detect extended LSBGs. We run \code{sep}\footnote{\url{https://sep.readthedocs.io/en/v1.1.x/}} \citep{Barbary2016} on the image cleaned as above. Based on the segmantation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$. This step reduces the number of blended sources. These values ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error.

@@

\subsection{Deblending}
A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or LSB outskirts of  stars and galaxies. In order to remove these objects from our sample, we perform non-parametric modeling for  each object using \code{scarlet}\footnote{\url{https://pmelchior.github.io/scarlet/}} \citep{Melchior2018}. \code{scarlet} is a deblending and modeling tool designed for multi-band data. It utilizes the color and morphology information to seperate blended sources. In the following, we briefly summarize how \code{scarlet} works, and we refer intersted readers to \citet{Melchior2018} for more details. In \code{scarlet}, each source in the scene $Y_i$ is described by a morphology matrix $S_i$ and a Spectral Energy Distribution (SED) vector $A_i$. The goal of modeling is to minimize the object function $f \propto \frac{1}{2}||\sum Y_i - P(\sum A_i S_i)||_2^{2}$ under certain constraints, where $P$ is the convolution with PSF. The morphology matrix of each source is limited to be within a bounding box. In this section, we assume that all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decreases from their centers to outskirts (monotonoicity constraint). Although not all galaxies satisfy the monotonicity constraint, it still provides an easy, sparse, and robust way to deblend overlapping sources. We refer to this modeling method as the ``vanilla scarlet''.

@@

\begin{enumerate}
\item \textbf{Peak detection.} We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate. Then we construct a detection image by taking a weighted average of the images in four separate bands. We take the total inverse variance as the weight for each band. This detection image is considered to be deeper than any single band image.

@@

\item \textbf{Model initialization and optimization}.
The deblending step is designed to deblend sources in the vicinity of the target object. The scene will contain both the target object and all the sources in its vicinity. Therefore, the sources being modeled is determined by how extended the target is. We estimate a bounding box based on the detection image, and include all the peaks inside this box to be modeled.

@@

\textbf{For bright sources? }

\item \textbf{Measurement.}
After running vanilla scarlet, we get non-parametric models of objects within the bounding box of the target. We take out the model of the target galaxy (as shown in Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \code{statmorph}\footnote{\url{https://statmorph.readthedocs.io/en/latest/}}\citep{statmorph}. The goal of this step is to remove false positives using various morphological and structural diagnostics.

@@

We also use Gini-M20 and CAS statistics. The Gini coefficient \citep{Abraham2003,Lotz2004} and M20 statistics quantify how concentrated/extended is the flux distribution across the image. The CAS statistics characterize the concentration ($C = 5\log_{10}(r_{80} / r_{20}$), asymmetry, and smoothness of the light distribution of the object. We refer the readers to \citet{statmorph} for more details on their definitions and implementations. The morphological and structural parameters are the same in different bands due to the construction of \code{scarlet} model.

We apply the following cuts:

\begin{itemize}
    \item Color:
    \[0.0 < g-i < 1.2,\ |(g-r) - 0.7\cdot (g-i)| < 0.25\]
    \item Size: \[2 \arcsec < r_e < 12 \arcsec\]
    \item Surface brightness: \[\mu_0(g) > 22.5,\ 23.0 < \mu_{\rm eff}(g) < 27.5,\]
    \item Morphology: 
    \begin{gather*}
        \varepsilon < 0.65,\ 1.8 < C < 3.5,\\
        \mathrm{Gini} < 0.70,\ M_{20} < -1.1,
    \end{gather*}
\end{itemize}

To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candiates.

The measured parameters here does not neccesarily represent the truth. We only use them to rule out false positives in a purely empirical way. The half-light radius is often too small because the cookie-cutter effect.

\end{enumerate}

Common false positives: why we want a deblending step
Why use scarlet: color info, non-par, monotonic, standard in future HSC, fast. Vanilla scarlet.
How does it work?

We design metric based on visual inspections for a random subset of LSBG candiates.

@@

Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands.

It is crucial to characterize the detection completeness in order to understand the intrinsic physical properties of the LSBG population. We performed a large suite of image simulation to derive the detection completeness. We inject $\sim 35,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline. This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}. However, we find no noticable difference between this method and the direct injection to coadd images.}. The mock galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$) to match the LSBG distribution in \citetalias{Greco2018}.

The detection completeness as a function of size and surface brightness is shown in the left panel of Figure \ref{fig:completeness}. The dependences of completeness on other parameters are very weak and are neglected in this work. The detection completeness falls steeply towards the high surface brightenss end and small end. This is because we manually excluded objects with high surface brightness in detection. 
\textbf{Explain it a little bit.}

\textbf{Wait... Is the detection efficiency map (jenny sent me) for S18A??? }

\subsection{Modeling and measurement error}

@@

\subsection{Matching with Milky-Way analogs}
The goal of this paper is to study the UDG population hosted by MW-like galaxies. However, the properties of MW itself vary in literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups. In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}). This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$. They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20-40 Mpc). In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$ ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA. We choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}). MW analogs selected using this definition is very close to those in SAGA but are slightly more massive than the ELVES hosts.

@@

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{subsec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. Then these LSBGs are associated with the host. We repeat this process for all hosts. If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius). In the end, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc. In the following, we perform a deblending step to effectively remove these spurious objects.

\subsection{UDG sample}
Remember to filter the UDG sample through the FDFC mask, and also remove duplicated objects.
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{size_distribution.pdf}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure}

@@

\section{Mock galaxy tests}

>>>>

\documentclass[twocolumn,astrosymb,twocolappendix]{aastex631}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\sbunit}{mag~arcsec$^{-2}$}

@@

\author[0000-0002-8873-5065]{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

\section{Methodology}
Given an overview of the steps here.

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for extended LSBGs in the first $\sim 200$ deg$^2$ of HSC survey. We continued the work in \citetalias{Greco2018} and extended the search to HSC \code{S18A} data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to \code{S16A}. We follow the same philosophy of source detection as in \citetalias{Greco2018}, but make several updates to accommodate \code{S18A} data. Below we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer interested readers to \citetalias{Greco2018} for more details. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} is also publically available.

@@

    %Unlike in \citetalias{Greco2018}, we do not smooth the image prior to thresholding. 
    After this step, there are still a number of small low surface brightness objects, which are typically marginally resolved galaxies or just pixels with high noise fluctuations. We detect and remove them since our main goal is to detect extended LSBGs. We run \code{sep}\footnote{\url{https://sep.readthedocs.io/en/v1.1.x/}} \citep{Barbary2016} on the image cleaned as above. Based on the segmantation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$. This step reduces the number of blended sources. These values ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error. We also get feedbacks from the completeness tests. Not smoothing the images gives us marginal improvement on completeness.

@@

\subsection{Deblending}\label{sec:deblending}
A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or LSB outskirts of  stars and galaxies. In order to remove these objects from our sample, we perform non-parametric modeling for  each object using \code{scarlet}\footnote{\url{https://pmelchior.github.io/scarlet/}} \citep{Melchior2018}. \code{scarlet} is a deblending and modeling tool designed for multi-band data. It utilizes the color and morphology information to seperate blended sources. In the following, we briefly summarize how \code{scarlet} works, and we refer intersted readers to \citet{Melchior2018} for more details. In \code{scarlet}, each source in the scene $Y_i$ is described by a morphology matrix $S_i$ and a Spectral Energy Distribution (SED) vector $A_i$. The goal of modeling is to minimize the object function $f \propto \frac{1}{2}||\sum Y_i - P(\sum A_i S_i)||_2^{2}$ under certain constraints, where $P$ is the convolution with PSF. The morphology matrix of each source is limited to be within a bounding box. In this section, we assume that all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decreases from their centers to outskirts (monotonoicity constraint). Although not all galaxies satisfy the monotonicity constraint, it still provides an easy, sparse, and robust way to deblend overlapping sources. We refer to this modeling method as the ``vanilla scarlet''.

@@

\subsubsection{Peak detection}
We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate. Then we construct a detection image by taking a weighted average of the images in four separate bands. We take the total inverse variance as the weight for each band. This detection image is considered to be deeper than any single band image.

@@

\subsubsection{Model initialization and optimization}
The deblending step is designed to deblend sources in the vicinity of the target object. The scene will contain both the target object and all the sources in its vicinity. Therefore, the sources being modeled is determined by how extended the target is. We estimate a bounding box based on the detection image, and include all the peaks inside this box to be modeled.

@@

\textbf{For bright sources? Cookie cutter effect}

\subsubsection{Measurement and false positive removal}\label{sec:non-par-measurement}
After running vanilla scarlet, we get non-parametric models of objects within the bounding box of the target. We take out the model of the target galaxy (as shown in Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \code{statmorph}\footnote{\url{https://statmorph.readthedocs.io/en/latest/}}\citep{statmorph}. The goal of this step is to remove false positives using various morphological and structural diagnostics.

@@

We also use Gini-M20 and CAS statistics. The Gini coefficient \citep{Abraham2003,Lotz2004} and M20 statistics quantify how concentrated/extended is the flux distribution across the image. The CAS statistics characterize the concentration ($C = 5\log_{10}(r_{80} / r_{20}$), asymmetry, and smoothness of the light distribution of the object. We refer the readers to \citet{statmorph} for more details on their definitions and implementations. The morphological and structural parameters are the same in different bands by design of the \code{scarlet} model.

To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candiates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics. We randomly selected 5,000 LSBG candidates that are matched with a host at $0.02 < z < 0.04$ (see Sec \ref{sec:match} for details). We run vanilla scarlet and measure morphological parameters for this subsample as described above. Then we generate color composite image for each object using HSC $griz$-bands with 0.5 arcmin on a side. The visual inspection was done by coauthors JEG, JG, SH, RB. Each object has been inspected by at least one person. Objects are classified into three types: \code{candy} (LSB galaxies with typicall dwarf galaxy features), \code{galaxy} (high surface brightness galaxies, or galaxies with spiral galaxy features), \code{junk} (false positives, including tidal streams, galaxy outskirts, and other artifacts). The difference between \code{candy} and \code{galaxy} can be quite ambiguous. In the end, we combine the votes from different persons as follows. An object is classified as \code{junk} if the number of votes as \code{junk} prevails the number of votes as \code{candy} and \code{galaxy}. For objects that are not \code{junk}, if the number of votes as \code{candy} is larger than that as \code{galaxy}, we assign this object as \code{candy}. Everything else is classified as \code{galaxy}. In total, there are 1146 \code{candies}, 2146 \code{galaxies}, and 1708 \code{junks}.

We use this visual inspection results to guide us on using the morphological and structural diagnostics. The distributions of \code{candy}, \code{galaxy}, and \code{junk} in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}. False positives (\code{junk}) are highlighted in red. Altough false positives are scattered all over the parameter space, a large fraction of them occupy regions with small size, extreme colors, very faint surface brightness, and large concentration and asymmetry. Therefore, we come up the following selection cuts to remove the false positives:
\begin{itemize}
    \item Color:
    \[0.0 < g-i < 1.2,\quad |(g-r) - 0.7\cdot (g-i)| < 0.25\]
    \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5,\]
    \item Morphology: 
    \begin{gather*}
        \varepsilon < 0.65,\quad \mathrm{Gini} < 0.70,\quad M_{20} < -1.1,\\
        \mathrm{Gini} < -0.136\cdot M_{20} + 0.37,\\
        1.8 < C < 3.5,\quad A < 0.8.
    \end{gather*}
\end{itemize}
These criteria (shown as dashed lines) effectively help us remove objects that are not likely being LSBGs of interest. The color cuts here is narrower than the one used in detection to further remove junks and background high redshift galaxies. It is worth noticing that we not only remove objects with small sizes, but also remove objects with large size, low surface brightness, and high concentration. This is because the scarlet model of some junks can be very concentrated in the center but also extends quite far. The slant demarcation line on Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to seperate merging galaxies and normal galaxies.

The distributions of objects after applying the above cuts are shown in the bottom panels of Figure \ref{fig:deblending_cuts}. After the cuts, 97\% of the \code{junk} are removed, but the majority (70\%) of \code{candy} still remains. The number of \code{galaxy} also drops by 75\%. This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample. The numbers used in the selection are purely driven by the visual inspection results.

It is worthy noticing that the scarlet modeling and non-parametric measurements is not designed to recover the intrinsic properties of the galaxies. They are only used as a diagnotic tool to remove false positives. Therefore, the half-light radius measured above does not correspond to the half-light radius of the galaxy itself, but merely a proxy. In reality, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects because the faint outskirts are typically not modeled well due to the non-parametric nature of vanilla scarlet and the monotonicity constraint. In Section \ref{sec:modeling}, we propose a method to better measure the size and total magnitude of LSBG using \code{scarlet}. We use the parameters measured in Section \ref{sec:modeling} for science.

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
	}
	\caption{Deblending cuts.}
	\label{fig:deblending_cuts}
\end{figure*}

Common false positives: why we want a deblending step

Why use scarlet: color info, non-par, monotonic, standard in future HSC, fast, high success rate. Vanilla scarlet.

@@

%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
After the source detection step and the deblending step, we obtain a sample of LSBG candidates where the fraction of false positives is very small.

It is crucial to characterize the completeness of both detection and deblending in order to understand our survey efficiency and the properties of the LSBG population. We performed a large suite of image simulation to derive the completeness. The overall completeness is a combination of detection and deblending completenesses. The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after cuts.

For the detection completeness, we inject $\sim 35,000$ (check number with Johnny) mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline. This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}. However, we find no noticable difference between this method and the direct injection to coadd images.}. The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$), resembling the LSBG distribution in \citetalias{Greco2018}. They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$) and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.

We find the detection completeness mainly depends the size and surface brightness of mock galaxy. As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes. It drops below 50\% when the surface brightness gets fainter than 27.5 mag arcsec$^{-2}$. We find negligible dependendce of completeness on \sersic{} index, color, and additional structure of galaxy (such as star-forming clumps). However, we find the completeness declines above ellipticity $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample. In this work, we neglect the dependences of detection completeness on parameters other than size and surface brightness.

\textbf{Need to update the completeness to the S18A version. Ping Johnny.}

For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them. The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$. Following the procedure described in Sec \ref{sec:deblending}, we measure the non-parametric sizes and surface brightnesses on the scarlet models of the mock galaxies. The deblending completeness is shown in the middel panel of Figure \ref{fig:completeness}. The deblending completeness is high at bright surface brightnesses, but starts to decline with increasing size and surface brightness. Mock galaxies fainter than $\overline{\mu}_{\rm eff}(g) > 27.5$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy. The deblending step is very effective on removing false positives, but at a cost of losing very LSB galaxies.

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The countours shows the 70\%, 50\%, and 20\% completenesses, respectively. \textbf{Also compare our completeness with other surveys.}

\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.}

\subsection{Modeling and measurement error}\label{sec:modeling}
Although vanilla scarlet does a good job on removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased. These measurements cannot be used to derive the physical properties of LSBGs.

The non-parametric modeling in \code{scarlet} assumes weak correlation between pixels by imposing the monotonicity constraint. This leads to two problems when applying vanilla scarlet to the LSBGs. First, since pixels are not strongly correlated in the model, the model cannot capture the galaxy light at very low signal-to-noise ratio. Second, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken. This issue, dubbed as the ``cookie-cutter effect'', can be seen in Figure \ref{fig:vanilla_scarlet_demo}. As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biases the measuremenets.

On the other side, parametric modeling imposes a very strong correlation on pixels. For example, using a 1-D light profile such as \sersic{}, pixels within an isophote are assumed to have the same intensity. Therefore, the signal-to-noise ratio in the outskirts is boosted by effectively combing the information from many pixels. The parametric model also does not suffer from the ``cookie-cutter'' issue.

A traditional way of doing parametric modeling is to first mask out contaminants based on the detection segmentation map, then fit a model to the masked image. However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018}. A possible solution to this problem is to model all the objects in the cutout simultaneously using parametric models (e.g., in DECaLS, \citealt{Dey2019}). In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}. To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model. In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized.

We use the Spergel light profile to model the LSBGs. The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to be convolved with a PSF.\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in Fourier space.} The surface brightness of a Spergel profile \citep{Spergel2010} has a form of
\begin{equation}
    \label{eq:spergel}
    I_\nu(r) = \frac{c_{\nu}^{2} L_{0}}{2\pi r_{0}^{2}} f_{\nu}\left(\frac{c_{\nu} r}{r_{0}}\right),
\end{equation}
where 
\begin{equation}
    f_{\nu}(u)=\left(\frac{u}{2}\right)^{\nu} \frac{K_{\nu}(u)}{\Gamma(\nu+1)},
\end{equation}
and $K_\nu(u)$ is the Modified Bessel function of the second kind. The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfyies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$. Similar to the \sersic{} index, the parameter $\nu$ (Spergel index) controls the concentration of the light profile. As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is interested to the study of LSBGs.

There are several changes in the modeling compared to the deblending step. First, we intialize a vanilla scarlet model for the target object as in Section \ref{sec:deblending}. Then we measure the half-light radius, total flux, and shape of the scarlet model. We use these numbers to initialize the Spergel profile. The size of the bounding box is also updated to be the maximum between 250 pixel and $10\, r_e$. Objects within this bounding box are included in the modeling, but only the target object is modeled by the Spergel profile. For the target, we still requires positivity constraint, as the mononicity is automatically satisfied.

After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take the $L_0$ as the total flux. The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}.

We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

@@

\subsection{Matching with Milky-Way analogs}\label{sec:match}
The goal of this paper is to study the UDG population hosted by MW-like galaxies. However, the properties of MW itself vary in literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups. In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}). This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$. They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20-40 Mpc). In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$ ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA. We choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}). MW analogs selected using this definition is very close to those in SAGA but are slightly more massive than the ELVES hosts.

@@

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. Then these LSBGs are associated with the host. We repeat this process for all hosts. If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius). In the end, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc. In the following, we perform a deblending step to effectively remove these spurious objects.

\subsection{UDG sample and UPG sample}
Remember to filter the UDG sample through the FDFC mask, and also remove duplicated objects.

Also append the catalog.

Plot the UDG and UPG population on the re-abs mag plane (Bovy book)

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{size_distribution.pdf}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure}

@@

\section{Spergel profiles}\label{ap:spergel}
